---
title: "Oranges"
output:
  html_document: default
  pdf_document: default
date: "2024-08-20"
---
## Orange Analysis
This is an analysis of Oranges, it's very scientific stuff.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
This is what the beginning of the file looks like. The file contains three columns.

```{r orange, echo=TRUE}
glimpse(Orange)
```

Here I have plotted the age vs circumference, and labeled the color by the tree.

```{r}
ggplot(Orange, aes(x = age,
                   y = circumference,
                   color = Tree)) +
  geom_point()
```

Now we will transition to looking at a dataset containing simple economic data. Lets view it's head:

```{r echo=TRUE}
glimpse(economics)
```
Lets try and see if there is a correlation between Personal Consumption Expenditures (pce) compares to Personal Savings Rate (psavert).

```{r echo=TRUE, warning=FALSE}
ggplot(economics, aes(x=psavert,
                      y=pce,
                      color=date)) +
  geom_point() +
  geom_smooth(method = lm)
```

